A Sample JFE Paper\footnotetext{Financial support from \ldots}

### 2018-03-15 Paper/Paper.tex
I added the abstract, conclusion, and results sections.

\vspace{-.2in}
\begin{abstract}
\noindent There's nothing very interesting here, but the format (achieved using the file \texttt{jfe.sty}) makes it suitable for publication in the \emph{Journal of Financial Economics} even if the content doesn't. Here's a nice, informative, single-spaced abstract.
\end{abstract}

@@

Through all robustness checks, the most constant result was that $\alpha = 1$. This has very important theoretical implications.

\section{Conclusion}\label{sec:Conclusion}

>>>>

\vspace{-.2in}
\begin{abstract}
\noindent 
In this paper a subset of parameters are estimated for a novel endogenous growth model. Building on previous work in which a distinction is made between different types of innovation, in this model firms choose endogenously between investing in abrupt or incremental innovations. This can lead to many interesting predictions regarding variation in R\&D investment choices over time. The model is fit to citation distributions for the entire US economy using structural estimation methods. The parameter estimates imply that there are no diminishing returns to incremental innovations, which has important theoretical implications.
\end{abstract}

@@

Through all robustness checks, the most constant result was that $\alpha = 1$. This has very important theoretical implications.  If accurate, it indicates that there are no diminishing returns to incremental innovations. This severely limits the strategic behavior predicted by the model. With $\alpha$ less than one, we would expect to see firms cycle between abrupt and incremental R\&D, as incremental innovations are initially very profitiable following an abrupt innovation, but eventually dry up. It is this dynamic that led to interesting predictions involving intertemporal productivity choice. With $\alpha$ equal to one, however, the profitability of incremental innovations is completely independent of the timing of the last abrupt innovation. Firms will always invest a constant amount in either type of innovation unless there are changes in the exogenous parameters of the model.

Our estimates of $\lambda_{abr, int} + \tau$ and $\lambda_{inc,0}$ are signficantly less interesting. As was expected, these estimates are sensitive to theoretical assumptions, especially the assumption that defines abrupt patents as a certain upper percentile of the citation distribution. When we assume that abrupt patents are the upper ten percent of patents, we find the ubrupt arrival rate $\lambda_{abr, int} + \tau$ to be between nine and ten times smaller than the incremental arrival rate $\lambda_{inc,0}$. When the cutoff is raised or lowered, the arrival rate parameters move in the direction that one would expect. Now, there was no guarantee that our estimates would match up with our assumptions this well; the patent citation distribution could have been shaped such that our ratio of lambdas was completely different from our assumed fraction of abrupt patents. Thus, these parameter estimates slighly increase our confidence in the model's ability to fit reality, but they do not have major theoretical implications.

\section{Conclusion}\label{sec:Conclusion}
The estimation presented in this paper is meant to be a first step toward the application our novel endogenous growth model. The model is an updated version of that developed by Akcigit and Kerr (2016), in which a distinction is made between abrupt and incremental innovations (that is, major innovations compared with minor improvements). In their model, however, firms invest in generic R\&D, which results in abrupt or incremental innovations according to an exogenous probability distribution. In our model, this feature is made endogenous; firms choose how much to invest in incremental versus abrupt R\&D. This can lead to many interesting predictions, including that firms may choose to accept a temporary productivity decline after realizing an abrupt innovation, which will eventually lead to higher productivity in the future.

For this paper, however, we focus on estimating a subset of the model's parameters using aggregate patent citation distributions. Akcigit and Kerr (2016) also use this as a first step in estimating their model. The citation distribution allows us to identify $\alpha$, a parameter that determines the rate of diminishing returns to incremental innovations, and $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$, a combined parameter that relates to the amount of abrupt relative to incremental innovations within the entire economy. The parameters are estimated using maximum likelihood estimation. The robustness of the estimates is investigated by using an alternative estimation scheme and by adjusting multiple theoretical assumptions.

Our most significant result, which also passes every robustness check, is that the parameter $\alpha$ is equal to one. This finding severely reduces the type of behavior predicted by our model, as it makes impossible any endogenous variation in R\&D investment over time. That being said, more work is needed before we can be confident in the result that $\alpha$ equals one. Most important is to test two key assumptions behind our identification scheme: that abrupt patents will receive a large number of total citations and that same-class citations are those that directly fall within the abrupt patent's technology cluster. Microdata on individual innovations and citation patterns could be used to investigate the legitimacy of these assumptions.

There are plenty more opportunities for future work. These include estimating the rest of the parameters in our model (which can be done by combining the patent database with compustat data) although the usefulness of the model is brought into question when $\alpha$ is equal to one. The result that $\alpha = 1$ leads to the testable prediction that there will be no correlation between the timing of  incremental and abrupt innovations; this could be checked in future empirical work. Regarding the overall fit of our model, more work needs to be done to explain the underestimate of the number of abrupt patents with zero citations. There is also room for a more sophisticated theoretical treatment of the heterogeneity in innovations, as the simple binary distinction between abrupt and incremental innovations does not seem to match the citation data well. Hopefully these and other future projects will continue to increase our understanding of innovation and economic growth.
